Neural Networks for Neural Tumors\\ \vspace{-0.6em} {\footnotesize Final Project for \textit{ECS 171 - Machine Learning} at UC Davis, with Professor Setareh Rafatirad}

### 2025-06-07 latex/draft.tex
remove comments

\large 
\section{\large Introduction (Complete)}

@@

\section{\large Literature Review (Complete)}

@@

\section{\large Dataset Description (Complete)}

@@

\section{\large Exploratory Data Analysis (1 page)}
% TODO: Complete but need to fix image placement so that EDA is on one consistent page

% EXAMPLE image in a column
% \begin{figure}[!ht]
%     \centering
%     \includegraphics[width=2in]{coconut.png}
%     \caption{this is a coconut}
%     \label{test image coconut}
% \end{figure}

% EXAMPLE image across two columns
% \begin{figure*}[!ht]
%     \centering
%     \includegraphics[width=3in]{coconut.png}
%     \caption{this is a coconut}
%     \label{coconut}
% \end{figure*}

% These two won't stay in the same row
% \begin{figure*}[!ht]
%     \centering
%     \includegraphics[width=1in]{ImagesPerClassTraining.png}
%     \caption{\large Images in the training dataset}
%     \label{Number of images per class in the training dataset}
% \end{figure*}

% \begin{figure*}[!ht]
%     \centering
%     \includegraphics[width=1in]{ImagesPerClassTesting.png}
%     \caption{\large Images in the testing dataset}
%     \label{Number of images per class in the testing dataset}
% \end{figure*}

% Both figures in one row
% TODO: Move these to be under EDA in the right spots
\begin{figure*}[!ht]
    \centering
    \includegraphics[width=0.49\textwidth]{ImagesPerClassTraining.png}
    \hfill
    \includegraphics[width=0.49\textwidth]{ImagesPerClassTesting.png}
    \caption{\large The dataset has a consistent number of training images across classes, except for ``no tumor". This should not be an issue because ``no tumor" imagery has much less variance. For testing, the distribution of images is more varied, but this does not affect model performance, since the model is not trained on this data.}
    \label{images-per-class}
\end{figure*}

@@

\section{\large Methodology (Complete)}

@@

\section{\large Experimental Results (Complete)}

@@

\section{\large Evaluation (Complete)}

@@

\section{\large Conclusion (Complete)}

@@

\section{\large Our Team (1 page)}

@@

\textbf{Richard}: Richard contributed to the project by assessing the performance of the three machine learning models. Based on these analyses, he provided the rationale for selecting the CNN as the final model. Additionally, he conducted comprehensive literature review to summarize key developments in the field, which  like Jonathan's findings, served as a foundational reference for the project.

>>>>

\large 
\section{\large Introduction}

@@

\section{\large Literature Review}

@@

\section{\large Dataset Description}

@@

\section{\large Exploratory Data Analysis}
\begin{figure*}[!ht]
    \centering
    \includegraphics[width=0.49\textwidth]{ImagesPerClassTraining.png}
    \hfill
    \includegraphics[width=0.49\textwidth]{ImagesPerClassTesting.png}
    \caption{\large The dataset has a consistent number of training images across classes, except for ``no tumor". This should not be an issue because ``no tumor" imagery has much less variance. For testing, the distribution of images is more varied, but this does not affect model performance, since the model is not trained on this data.}
    \label{images-per-class}
\end{figure*}

@@

\section{\large Methodology}

@@

\section{\large Experimental Results}

@@

\section{\large Evaluation}

@@

\section{\large Conclusion}

@@

\section{\large Our Team}

@@

\textbf{Richard}: Richard contributed to the project by assessing the performance of the three machine learning models. Based on these analyses, he provided the rationale for selecting the CNN as the final model. Additionally, he conducted comprehensive literature review to summarize key developments in the field which served as a foundational reference for the project.
